Flabby and injective objects in toposes

### 2022-02-13 paper-flabby-objects.tex
Reference to Kempf
to do
Explanation of "over-locale"

Let~$X$ be a locale and let~$f : Y \to X$ be an over-locale. By the fundamental
relation between locales and topological spaces, this situation arises
for instance, when given a sober topological space and a topological
space over it, as is often the case in algebraic topology or algebraic
geometry. Let a sheaf~$\O_Y$ of rings on~$Y$ be given. Then the
traditional way to define the \emph{higher direct images} of a sheaf~$E$
of~$\O_Y$-modules is to pick an injective resolution~$0 \to E \to I^\bullet$
and set~$R^n f_*(E) \defeq H^n(f_*(I^\bullet))$.

@@

Higher direct images are pictured as a ``relative'' version of sheaf
cohomology. Due to the result that injectivity of sheaves of modules can be
characterized in the internal language, we can give a precise
rendering of this slogan: We can understand higher direct images as
internal sheaf cohomology.

@@

Can this issue be remedied by employing flabby resolutions
instead of injective ones? Classically, it is known that they can be used in
their stead. There are, however, two problems with this
suggestion. Firstly, all proofs known to us that flabby sheaves are
acyclic for the global sections functor require Zorn's lemma. This problem might
be mitigated by relying on the substitute property discussed
following Scholium~\ref{scholium:exact-as-presheaves}. \XXX{XXX}

@@

>>>>

Let~$X$ be a locale and let~$Y$ be a locale over~$X$, that is, a morphism~$f : Y \to X$ of locales. By the fundamental
relation between locales and topological spaces, this situation arises
for instance, when given a sober topological space and a topological
space over it, as is often the case in algebraic topology or algebraic
geometry. Let a sheaf~$\O_Y$ of rings on~$Y$ be given. Then the
traditional way to define the \emph{higher direct images} of a sheaf~$E$
of~$\O_Y$-modules is to pick an injective resolution~$0 \to E \to I^\bullet$
and set~$R^n f_*(E) \defeq H^n(f_*(I^\bullet))$~\cite[Tag~01DZ]{stacks-project}.

@@

Higher direct images are pictured as a ``relative'' version of sheaf
cohomology. Due to the result that injectivity of sheaves of modules can be
characterized in the internal language, we can give a precise
rendering of this slogan: \emph{Higher direct images are
internal sheaf cohomology.}

@@

Can this issue be remedied by employing flabby resolutions
instead of injective ones? Classically, it is known that they can be used in
their stead. For instance, George Kempf developed the foundations of the
cohomology of quasicoherent sheaves on this premise~\cite{kempf:cohomology}. There are, however, two problems with this
suggestion. Firstly, all proofs known to us that flabby sheaves are
acyclic for the global sections functor require Zorn's lemma. This problem might
be mitigated by relying on the substitute property discussed
following Scholium~\ref{scholium:exact-as-presheaves}. \XXX{XXX}

@@

XXX: injective as module implies functionally flabby

FUTURE:

* Does "flabby sheaves are acyclic on all locales" imply Zorn?
